Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-06 Article/ici_submm_cloudcorr.tex
included suggestions from Patrick

@@

Identification of cloud affected observations is indispensable for both clear-sky and all-sky Numerical Weather Prediction (NWP) systems. In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to a present sensor: MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction. In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve. On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact. Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering; and the resulting error distributions are almost symmetric with very low spread. The methodology also works well when only one of the higher frequencies (325\,GHz) is available. Except for the lowest peaking channel, using sub-mm observations results in error distributions with standard deviation less than the measurement noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for each case individually. Despite individual variations for each channel, the predictions exhibit a higher uncertainty when the test data includes the ``out of distribution'' cases. In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.

@@

Despite their broad usage, these filtering methods aim at partial removal of cloud contamination. The residual cloud impact can have some drawbacks. For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean. This bias will translate to a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors. However this artificial suppression of observations diminishes the impact of observations.  The alternative is to apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the uncertainty to assign to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors have been provided. Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.

@@

The approach is demonstrated with use of 89 and 150\,GHz channels (following
\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). The focus on sub-mm channels is motivated by several reasons.  Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors. For high altitude cirrus clouds, the these frequencies have a stronger signal than 183\,Ghz. In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher. Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing
data and applying ICI data for cloud filtering has not earlier been discussed. It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.

A description of data and QRNN is provided in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the applicabity of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.
\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

@@

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.311    & 2000	&		\\
		AWS-33	&	178.811    & 2000 	&	\\
		AWS-34	&	180.311    & 1000 	&	\\
		AWS-35	&	181.511    & 1000 	&	 \\
		AWS-36	&	182.311    & \phantom{0}500  &	 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The main objective of AWS will be to improve the representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts. AWS will will have channels receiving frequencies around 89.00\,GHz, 165.5\,GHz, 183.31\,GHz, 229.00\,GHz and 325.15\,GHz. For a detailed description of the AWS channels see \citet{eriksson2020study}.

In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

\subsection{Simulations}
%
MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system. RTTOV and RTTOV-SCATT are used to calculate the radiances in clear-sky and all-sky conditions, respectively. For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used. Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$. With this filter we have 340\,000 cases for each frequency.

ICI and AWS frequencies are simulated with ARTS. Cloudsat profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases are simulated. All ICI frequencies are simulated directly. For AWS, 140\,000 cases are simulated. Forward simulations are performed for 21 monochromatic frequencies, and later these frequencies are interpolated to a finer grid to get the AWS channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The noise free simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest are used for testing.

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature $\ynfcs$ at a given $183\unit{GHz}$ channel from a vector of
cloud-contaminated observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
networks (QRNN) can be used to solve these type of problems. Instead of a point
prediction, as it is typically performed in regression problems, QRNNs learn to
predict a vector of quantiles, which can be used to approximate the distribution
of the predicted quantity conditional on the network inputs. Using QRNNs to
perform probabilistic cloud correction thus not only allows deriving an estimate
for $\ynfcs$ but also for the error of the corrected observations.

@@

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyperparameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The output in both configurations is NFCS value for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

\begin{enumerate}
	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels. Additional data is included, if relevant. No other 183\,GHz channel is included.

	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input. Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account; but the main difference is the concurrent utilisation of all 183\,GHz frequencies.      
\end{enumerate}

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the dataset, respectively.

@@

All evaluation results described in the study have been made on the testing data.

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the methodology is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

\subsection{Experiments}
%
For MWHS-2, multiple experiments using both QRNN configurations are performed. With different experiments we aim to delve into the sensitivity of the method to different input channels:

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied. In this experiment, the training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}. For channels 11 and 12 the performance of QRNN is comparable to scattering index, albeit 30\% of the observations are rejected in the latter. For channels 13 and 15, the error statistics obtained with SI are slightly inferior. The filtering with B183 is also partial for all channels, but is poorer than SI.

>>>>

\sloppy

@@

Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems. In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to a present sensor: MWHS-2 (MicroWave humidity sounder 2). With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction. In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve. On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact. Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering. The resulting error distributions are almost symmetric with very low spread. The methodology also works well when only one of the higher frequencies (325\,GHz) is available. Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for each case individually. Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels. In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.

@@

Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean. This bias will translate to a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors. However this artificial suppression of observations diminishes the impact of observations. The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the assignment of uncertainty to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors have been provided. Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.

@@

The approach is demonstrated with use of 89 and 150\,GHz channels (following
\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as Artic Weather Satellite (AWS); presented below). The focus on sub-mm channels is motivated by several reasons.  Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger signal than 183\,Ghz. In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher. Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing data and applying ICI data for cloud filtering has not earlier been discussed. It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.

A description of data and QRNN is provided in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the applicability of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}). The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global NWP models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

@@

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.311    & 2000	&		\\
		AWS-33	&	178.811    & 2000 	&	\\
		AWS-34	&	180.311    & 1000 	&	\\
		AWS-35	&	181.511    & 1000 	&	 \\
		AWS-36	&	182.311    & \phantom{0}500  &	 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as European Space Agency (ESA)
Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels shall be included. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted.

\subsection{Simulations}
%
MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system. RTTOV (Radiative Transfer for TOVS, \citet{saunders2018update} and RTTOV-SCATT \citep{bauer2006rttovscat} are used to calculate the radiances in clear-sky and all-sky conditions, respectively. For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used. Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$. With this filter we have 340\,000 cases.

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest are used for testing.

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature \todo{$\ynfcs$, define it} at a given $183\unit{GHz}$ channel from a vector of
all-sky observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

As has been shown in \citet{pfreundschuh:aneur:18}, QRNN can be used to solve these type of problems. Instead of a point prediction, as it is typically performed in regression problems, QRNNs learn to
predict a vector of quantiles, which can be used to approximate the distribution
of the predicted quantity conditional on the network inputs. Using QRNNs to
perform probabilistic cloud correction thus not only allows deriving an estimate
for $\ynfcs$ but also for the error of the corrected observations.

@@

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyper-parameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

\begin{enumerate}
	\item QRNN-single: In this configuration, the training input comprises of  all-sky brightness temperatures from the target 183\,GHz channel and other channels. Additional data is included, if relevant. No other 183\,GHz channel is included.

	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz frequencies are included.      
\end{enumerate}

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

All evaluation results described in the study have been made on the test dataset.

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channel. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the methodology is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

\subsection{Experiments}
%
\label{sec:QRNN_expt_MWHS}
For MWHS-2, multiple experiments using both QRNN configurations are performed. With these we aim to delve into the sensitivity of the method to different input channels:

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels are used to identify the cloud affected data for ATMS and MWHS-2 \citep{geer2015scatteringindex}. To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied. In this experiment, the training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}. For channel 11 the performance of QRNN is comparable to both SI and B183. Similar is the case with channel 12, though the results from B183 are slightly poor. Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well. The major caveat is the rejection of clear cases. With comparable accuracy, the fraction of rejection in SI is approx. 30\% in comparison to approx. 3\% in B183. For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN. The results with B183 are even worse. For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact. Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.
